Stochastic modeling of EGS using continuum-fracture approach and multilevel Monte Carlo

### 2019-07-18 paper.tex

Number of wells: 2 \\
Depth: 5 km \\
Distance: 200 m \\
Well radius: 15 cm \\
Length of open part of wells: 60 m \\

@@

In our model we consider the cube $600 \times 600 \times 600$ m around the lower well ends, from which two cylinders of radius 10 m and height 60 m are removed.
These represent the surrounding of the open well parts.
The reason for using 10 m radius instead of the real well radius is to keep the number of necessary mesh elements reasonable.
The wells are connected by three fractures, two of them intersecting the cylinders and one intersecting the first two fractures.

On the surface of the artificial cylinders we shall extrapolate the value of piezometric head as follows: Given value $H_w$ of piezometric head at the well surface (with radius $r_w$) we assume that the piezometric head in the vicinity of the well is the function of the distance $d_w$ to the well axis:
\eq{\label{eq:H_log} H(\xx) = H_w\frac{\log d_w(|\xx|)}{\log r_w}. }
Then, on the surface of the cylinder at radius $r_c$ we impose the Robin condition in the Darcy flow equation:
\eq{\label{eq:H_robin} k\nabla H\cdot\nn = \sigma(H-H_w), }
where $\nn$ stands for the unit outward normal vector.
From \eqref{eq:H_log} and \eqref{eq:H_robin} we obtain the transition coefficient
\[ \sigma = \frac{k}{r_c}\left|\frac{\log r_c}{\log r_w}\right| \]
whose value depends on the hydraulic conductivity.

@@

Boundary conditions:
\begin{itemize}
\item piezometric head $10^3$ m on surface of wells (including the intersections with fractures)
\item piezometric head 0 m on lateral sides of the box (MOZNA BY MELO BYT I NAHORE A DOLE?)
\item no fluid flow through bottom and top part of the box and fracture tips
\item zero displacement on bottom part of the box, zero displacement in the direction orthogonal to box sides
\item zero traction elsewhere
\end{itemize}

@@

Boundary conditions:
\begin{itemize}
\item piezometric head $\pm10^2$ m on surface of wells ($+$ on the injection well, $-$ on the production well)
\item piezometric head 0 m on lateral sides of the box (MOZNA BY MELO BYT I NAHORE A DOLE?)
\item no flux on bottom and top part of the box and on fracture tips
\item temperature $15\ ^\circ$C on surface of injection well (ZDE BY SE MELA UDELAT APROXIMACE DIRICHLETA ROBINEM PODOBNE JAKO V PROUDENI Z NEJAKEHO ANALYTICKEHO RESENI)
\item initial temperature on lateral sides of the box where fluid flows into the box
\item no heat flux through bottom and top part of the box and fracture tips
\end{itemize}

>>>>

Number of wells: 2 \\
Depth: 5 km \\
Distance: 200 m \\
Well radius: $\rho = 15$ cm \\
Length of open part of wells: $l=60$ m \\

@@

In our model, we consider pair of vertical wells with the radius $\rho=0.15$ m in the distance $D=200$ m. The open part of the length $L=60$ m is in the depth $5000$ m. The cube $600 \times 600 \times 600$ m around open part is considered as the computing domain.

{\bf The test geometry:}The wells are connected by three fractures, two of them intersecting the cylinders and one intersecting the first two fractures.

\subsection{Analytical models in the vicinity of the wells}
In order to keep mesh size treatable, we replace the Dirichlet boundary condition for the pressure applied on the open part of the well by the Robin type condition:
%
\eq{\label{eq:H_robin} k\nabla H\cdot\nn = \sigma(H-H_w), }
%
applied on the cut-out cylinders of the radii $R=10$ m. We assume the constant conductivity $k$ in the vicinity of wells. The parameter $\sigma$ is determined from the analytical radially symmetric solution
of the steady Darcy flow problem with a point source:
\[
    h(r) = -\alpha \log (r) + \beta
\]
where $r$ is the distance from the well and $\alpha$, $\beta$ are arbitrary constants.
The flux through the cylinder of the radius $r$ and the length $L$ is the constant
\[  
    Q = -2\pi \rho L k h'(\rho) = 2\pi L k \alpha,
\]
where we have used the Darcy law with the conductivity $k$. Now we use the analytical solution to fit the Robin type boundary condition:
\[
    Q = 2\pi R l \sigma (h(\rho) - h(R)) = 2\pi R l \sigma \alpha \log(R/\rho),
\]
which combined with previous equality determines $\sigma$ as:
\[ 
    \sigma = \frac{k}{R\log(R/\rho)}.
\]

Since the heat transfer is dominated by the convection in the vicinity of the wells the temperature in the well is transported to the surface of the cut-off cylinders or vice verse in the time $t_0 = R/q$ which for the observed volume fluxes $Q\sim 1$ l/s is about $100$ days. This is negligible with respect to the total lifetime of the heat exchanger.

{\bf Original JS idea:}
This flux has to be equal to the flux through the surface of the extended well cylinders:
\[
    Q = 2\pi R l q,\quad q=\sigma(h_\rho - h)
\]
On the surface of the artificial cylinders we shall extrapolate the value of piezometric head as follows: Given value $H_w$ of piezometric head at the well surface (with radius $r_w$) we assume that the piezometric head in the vicinity of the well is the function of the distance $d_w$ to the well axis:
\eq{\label{eq:H_log} H(\xx) = H_w\frac{\log d_w(|\xx|)}{\log r_w}. }
Then, on the surface of the cylinder at radius $r_c$ we impose the Robin condition in the Darcy flow equation:
where $\nn$ stands for the unit outward normal vector.
From \eqref{eq:H_log} and \eqref{eq:H_robin} we obtain the transition coefficient
\[ \sigma = \frac{k}{r_c}\left|\frac{\log r_c}{\log r_w}\right| \]
whose value depends on the hydraulic conductivity.

@@

Boundary conditions:
\begin{itemize}
\item piezometric head $10^3$ m on surface of wells (including the intersections with fractures)
\item piezometric head 0 m on lateral sides of the box
\item no fluid flow through bottom and top part of the box and fracture tips
\item zero displacement on bottom part of the box, zero displacement in the direction orthogonal to box sides
\item zero traction elsewhere
\end{itemize}

@@

Boundary conditions:
\begin{itemize}
\item piezometric head $\pm10^2$ m on surface of wells ($+$ on the injection well, $-$ on the production well)
\item no flux on the external boundary of the box and on fracture tips
\item temperature $15\ ^\circ$C on surface of injection well (ZDE BY SE MELA UDELAT APROXIMACE DIRICHLETA ROBINEM PODOBNE JAKO V PROUDENI Z NEJAKEHO ANALYTICKEHO RESENI)
\item initial temperature on lateral sides of the box where fluid flows into the box
\item no heat flux through bottom and top part of the box and fracture tips
\end{itemize}
